Combinatorics of the geometry of Wilson loop diagrams

### 2019-02-07 General WLD combinatorics.tex
fixed one tiny typo that none the less affected meaning

\begin{thm}\label{thm denom}
  Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace. Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), the $R$ of Algorithm~\ref{alg WLD to denom via GN}, which is also up to scalar multiple the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.  
\end{thm}

>>>>

\begin{thm}\label{thm denom}
  Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace. Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is the $R$ of Algorithm~\ref{alg WLD to denom via GN}, which is also, up to scalar multiple, the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.  
\end{thm}
